---
title: "Introduction to articulated"
author: "Fredrik Nylén"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to articulated}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

The **articulated** package provides tools for assessing speech articulation performance from acoustic data with emphasis on clinical and research applications.

### Key Features

- **High Performance**: Rcpp implementations provide 10-100x speedup
- **Comprehensive Metrics**: 30+ features covering rhythm and vowel space
- **superassp Integration**: Seamless workflow with superassp package
- **Batch Processing**: Parallel processing for large datasets
- **Clinical Focus**: Metrics validated in speech pathology research

## Quick Start

```{r eval=FALSE}
library(articulated)
library(superassp)

# Extract all features from audio file
features <- lst_articulation("speech.wav")

# View results
print(features$vsa)   # Vowel space area
print(features$npvi)  # Rhythm variability
```

See `vignette("superassp-integration")` for detailed workflows.
